My title

### 2024-03-08 paper/paper.qmd
model (n=1000) and another graph

library(rstanarm)
political_preferences <-
  readRDS(file = here::here("models/political_preferences.rds"))

# first_model <-
#   readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false
install.packages("modelsummary")

# Load the modelsummary package
library(modelsummary)

@@

>>>>

political_preferences <-
  readRDS(file = here::here("models/political_preferences.rds"))

political_preferences2 <-
  readRDS(file = here::here("models/political_preferences2.rds"))

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary(
  list(
    "Support Biden" = political_preferences2
  ),
  statistic = "mad"
  )

```{r}
modelplot(political_preferences2, conf_level = 0.9) +
  labs(x = "90 per cent credibility interval")
```
